A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Add citations
Add additional references
Add additional citation
Add additional citations
Fix syntax
Add basic structure and first version of abstract

\begin{abstract}
Tbd.
\end{abstract}

\section{Introduction}
Tbd.

@@

%\bibliographystyle{abbrv}
%\bibliography{paper}

>>>>

\begin{abstract}
This paper serves as a survey on \textit{ordered binary Decision diagrams}
(\textit{OBDDs}). It provides an overview of the representation of OBDDs, the
operations which can be applied efficiently, some aspects when implementing them
as well as their limitations and how to probably overcome them by using
alternative representations. No new results or insights are provided.  [TO BE
REVISED].
\end{abstract}

\section{Introduction}
\label{sec:introduction}

Tbd.

\section{Representation Basics}
\label{sec:representation-basics}

Tbd.

\subsection{Reducing and Ordering BDDs}
\label{subsec:reducing-and-ordering-bdds}

Tbd.

\section{Efficient Operations}
\label{sec:efficient-operations}

Tbd.

\section{Implementational Aspects}
\label{sec:implementation-aspects}

Tbd.

\subsection{Dynamic Variable Ordering}
\label{subsec:dynamic-variable-ordering}

Tbd.

\section{Limitations}
\label{sec:limitations}

Tbd.

\section{Alternative Representations}
\label{sec:alternative-representations}

Tbd.

\section{Citations (temporary)}

\noindent
\par
LEE59\cite{LEE59}, AKERS78\cite{AKERS78}, BRYANT86\cite{BRYANT86},
\par
BRACE90\cite{BRACE90}, BRYANT91\cite{BRYANT91}, BRYANT92\cite{BRYANT92},
\par
RUDELL93\cite{RUDELL93}, BRYANT95\cite{BRYANT95}, BOLLIG96\cite{BOLLIG96},
\par
ANDERSEN97\cite{ANDERSEN97}, WOELFEL01\cite{WOELFEL01}

@@

\bibliographystyle{abbrv}
\bibliography{paper}
